\sysfull

### 2018-04-16 paper/intro.tex
little edits to intro and abstarct

\begin{wrapfigure}{t!}{0.5\textwidth}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/intro-figure.pdf}
    \caption{Task coalescing at runtime reduces time and energy overhead in task-based intermittent programming models by performing fewer commits (denoted as \textt{cmt} in the figure). On the other hand, task splitting reduces wasted computation and enables termination for bigger tasks.}
    \label{fig:coalesce}
\end{wrapfigure}

>>>>

\begin{wrapfigure}{t!}{0.5\textwidth}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/intro-figure.pdf}
    \caption{Task coalescing at runtime reduces time and energy overhead in task-based intermittent programming models by performing fewer commits (denoted as \texttt{cmt} in the figure). On the other hand, task splitting reduces wasted computation and enables termination for bigger tasks.}
    \label{fig:coalesce}
\end{wrapfigure}
